master thesis

### 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
Paper - Abstract - update

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter*{Abstract}
  With increasing amounts of data, new investigations are also possible in phylogeny. This work 
    deals with the ancestral state reconstruction of parasitism in the tree of life of eukaryotes. 
    To predict states of the unknown species and estimate origins and losses of parasitism. \\
  We performed an analysis of existing algorithms and applied a Sankoff maximum parsimony algorithm 
    using the R package Castor \cite{Louca2017}. \\
  The challenge here is the size of the tree and the little information about it. On the one hand, 
    such a large phylogenetic tree is not completely existent, and we therefore work with a synthesis 
    tree of OTL \cite{Hinchliff2015}, which is highly multifurcated. On the other hand, for the 
    approximately 300 000 leaf nodes we found only for $\approx 4,3\%$ information whether they are 
    parasitic or free-living species (obtained from the GloBI database \cite{Poelen2014}).
\tableofcontents
\clearpage

>>>>

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter*{Abstract}
  With increasing amounts of data, new investigations are also possible in phylogeny. This study 
    deals with the ancestral state reconstruction of parasitism in the tree of life of eukaryotes. 
    We predict unknown states of species and estimate origins and losses of parasitism. \\
  We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
    using the R package \textit{Castor} \cite{Louca2017}. \\
  The challenge here is the size of the tree and the little information about it. \\
  Such a large phylogenetic tree does not completely exist and therefore we work with a synthesis 
    tree of OTL \cite{Hinchliff2015} which is highly multifurcated. \\
  For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
    \cite{Poelen2014} whith we used for this, we could only collect 25,992 parasitic and 34,879 
    free-living species. It follows that we have only $\approx 2.4\%$ state information. \\

  Nevertheless, the analysis of our results revealed that our forecast is largely credible. \\
  We have compared the results of some subtrees with known knowledge (Chordata, Nematoda, 
    Platyhelminthes and Apicomplexa) and except for the Nematoda the results looked very good. In 
    the case of nematodes, the data situation is strongly shifted to the few parasites. \\
  Our number of origins we could partly compare with the results of Sara B. Weinstein and Armand M. 
  Kuris from their article \textit{Independent origins of parasitism in Animalia} \cite{Weinstein2016} 
    and have come to a similar magnitude. They identified 223 parasitic origins in Metazoa and we 
    were able to estimate about 300 origins. \\

\tableofcontents
\clearpage
